How crisis affect the low-income and high-income economies differently

### 2024-04-17 paper/paper.qmd
fixing format
Working on appendix

Lastly, the data presented in @fig-inflation, @fig-gdp-growth, and @fig-lf, I observed that high-income countries shared similar economic performance trends. Despite not necessarily excelling in all economic indicators than the low-income countries, however, these countries generally maintain a more stable economic condition, with only a few exceptions or outliers noted. Also the overall economic performance in 2021 are better than in 2020.

@@

stargazer(highmodel, type = "text",
          title = "Summary of High Income Model",
          align = TRUE,
          out = "model_summary.txt")
```
The high income-countries have an overall better performance than the low-income countries: 
The GDP Growth (`gdp_growth`) coefficient is 567.121 with a standard error of 244.367, significant at the p<0.05 level. This suggests a positive and statistically significant relationship between GDP growth and GNI per capita in high-income countries, indicating that economic growth positively impacts income levels. Then the Unemployment Rate (`unem_rate`) coefficient is -849.519 with a standard error of 350.854, significant at the p<0.05 level. This indicates a significant negative impact of higher unemployment rates on GNI per capita, suggesting that unemployment is a critical economic issue affecting income in high-income countries. The Labor Force Participation Rate (`lf_par_rate`) coefficient is 433.735 with a standard error of 229.487, significant at the p<0.1 level. This shows a positive relationship between labor force participation and GNI per capita, though the relationship is less statistically significant. The Trade Percentage of GDP (`trade_per`) coefficient is 59.875 with a standard error of 22.554, significant at the p<0.01 level. This indicates a robust positive relationship, suggesting that trade openness contributes significantly to GNI per capita in high-income countries. Lastly, the Inflation (`inflation`) coefficient is -2,799.239 with a standard error of 600.123, significant at the p<0.01 level. This suggests a strong negative impact of inflation on GNI per capita, indicating that higher inflation rates are detrimental to income levels.

@@

The negative coefficient for GDP growth in low-income countries was expected however, it was not significant. For high-income countries, GDP growth shows a positive and significant impact, indicating robust economic dynamics where growth directly enhances national income levels. Also the high income countries showed a significant stronger positive relationship on labour force participation rate and trade as a share of GDP.

@@

\appendix

@@

>>>>

Lastly, the data presented in @fig-inflation, @fig-gdp-growth, and @fig-ur, I observed that high-income countries shared similar economic performance trends. Despite not necessarily excelling in all economic indicators than the low-income countries, however, these countries generally maintain a more stable economic condition, with only a few exceptions or outliers noted. Which I will be expecting the data to be normally distributed. Also the overall economic performance in 2021 are better than in 2020.

@@

stargazer(highmodel, type = "text",
          title = "Summary of High Income Model",
          align = TRUE,
          out = "model_summary.txt")
```

The high income-countries have an overall better performance than the low-income countries: 
The GDP Growth (`gdp_growth`) coefficient is 567.121 with a standard error of 244.367, significant at the p<0.05 level. This suggests a positive and statistically significant relationship between GDP growth and GNI per capita in high-income countries, indicating that economic growth positively impacts income levels. Then the Unemployment Rate (`unem_rate`) coefficient is -849.519 with a standard error of 350.854, significant at the p<0.05 level. This indicates a significant negative impact of higher unemployment rates on GNI per capita, suggesting that unemployment is a critical economic issue affecting income in high-income countries. The Labor Force Participation Rate (`lf_par_rate`) coefficient is 433.735 with a standard error of 229.487, significant at the p<0.1 level. This shows a positive relationship between labor force participation and GNI per capita, though the relationship is less statistically significant. The Trade Percentage of GDP (`trade_per`) coefficient is 59.875 with a standard error of 22.554, significant at the p<0.01 level. This indicates a robust positive relationship, suggesting that trade openness contributes significantly to GNI per capita in high-income countries. Lastly, the Inflation (`inflation`) coefficient is -2,799.239 with a standard error of 600.123, significant at the p<0.01 level. This suggests a strong negative impact of inflation on GNI per capita, indicating that higher inflation rates are detrimental to income levels.

@@

The negative coefficient for GDP growth in low-income countries was expected however, it was not significant. For high-income countries, GDP growth shows a positive and significant impact, indicating robust economic dynamics where growth directly enhances national income levels. Also the high income countries showed a significant stronger positive relationship on labour force participation rate and trade as a share of GDP. 
From @fig-qq-low we could see that the observations were mostly separated and with multiple outliers which indicates that we have a low sample size also deviates from normality. Which shows that for the low-income countries model, it has potentially leading to skewed or biased estimates.
From @fig-qq-high the points on the Q-Q plot fall approximately along a straight line, suggesting that the residuals follow a normal distribution. Which it also has less outliers compared with the low-income model. It also furthe confirm that the residuals are normally distributed, supporting the validity of the least squares regression assumptions.

@@

@@

```{r}
#| label: fig-qq-low 
#| fig-cap: Q-Q Plot of the low-income model
#| echo: false
#| warning: false
#| message: false

# Q-Q Plot
qqnorm(residuals(log_lowmodel), main = "Q-Q Plot of the low-income model")

```

```{r}
#| label: fig-qq-high
#| fig-cap: Q-Q Plot of the high-income model
#| echo: false
#| warning: false
#| message: false

# Q-Q Plot
qqnorm(residuals(log_highmodel), main = "Q-Q Plot of the high-income model")
```
